\textbf{{\Large {Recursive algorithms, branching coefficients and applications}}}

### 2010-05-31 AffineLieAlgebras/InformalNotes/article.tex
Minor changes
Image work+typo fixes

All the cases are listed in the table \ref{tab:diagrams}.
\begin{table}[ph]
\label{tab:diagrams}
\noindent  \centering{
\begin{tabular}{|l|l|l|l|}
  \hline
  $\mathfrak{g}$ & Extended diagram of the algebra $\mathfrak{g}$ & Diagrams of the subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ \\
  \hline
  $A_n$ & \includegraphics{A_series_ext_diag.pdf} & \includegraphics{A_series_ext_split.pdf} \\
  \hline
  $B_n$ & \includegraphics{B_series_ext_diag.pdf} & \includegraphics{B_series_ext_split.pdf} \\
  \hline
  $C_n$ & \includegraphics{C_series_ext_diag.pdf} & \includegraphics{C_series_ext_split.pdf} \\
  \hline
  $D_n$ & \includegraphics{D_series_ext_diag.pdf} & \includegraphics{D_series_ext_split.pdf} \\
  \hline
\end{tabular}
\caption{Subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ for the classical series}}
\end{table}

@@

For the coefficient function $s\left( \gamma \right) $ define the carrier $\Phi _{\frak{a%
}\subset \frak{g}}\subset P_{\frak{a}}$:
\begin{equation}
\Phi _{\frak{a}\subset \frak{g}}=\left\{ \gamma \in P_{\frak{a}}\mid s\left(
\gamma \right) \neq 0\right\} .  \label{phi-d}
\end{equation}
From the obtained equation for the formal elements,
\begin{multline}
  \label{eq:16}
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
  = -\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s\left( \gamma \right) e^{-\gamma }\sum_{\lambda \in P_{\frak{a}}}
  k_{\lambda }^{\left( \mu \right) }e^{\lambda } \\
  =-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}}\sum_{\lambda \in P_{\frak{a}}}s\left( \gamma \right) k_{\lambda }^{\left( \mu \right)}e^{\lambda -\gamma }
\end{multline}
we can deduce the following property of the anomalous branching coefficients,
\begin{equation}
  \label{eq:17}
   \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
   \sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s(\gamma)\; k^{(\mu)}_{\xi+\gamma}=0;\quad \xi\in P_{\mathfrak{a}}.
\end{equation}

@@

\subsubsection{Embedding of $B_2$ into $B_4$}
\label{sec:someth-high-dimens}
Consider the regular embedding $B_2 \longrightarrow B_4$.
We calculate the branching coefficients for the fundamental vector representation of $B_4$.
The corresponding Dynkin diagrams are in the Figure \ref{fig:dynkin}.
\begin{figure}[ph]
  \centering
  \includegraphics[width=60mm]{B4_B2_2A1.pdf}
  \caption{Dynkin diagrams}
  \label{fig:dynkin}
\end{figure}

@@

The result of this procedure is shown in the Figure \ref{fig:B4B2anom}.
\begin{figure}[h!tb]
    \includegraphics[width=150mm]{B4_B2_anom_points.pdf}
  \caption{Anomalous weights with the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:B4B2anom}
\end{figure}

\begin{figure}[h!tb]
  \includegraphics[width=130mm]{B4_B2_fan.pdf}
  \caption{Fan for $B_2\subset B_4$}
  \label{fig:B4B2Fan}
\end{figure}
Applying the recurrent relation (\ref{recurrent-relation}) we obtain the
following branching coefficients:
\begin{equation}
  \label{eq:24}
  \pi_{\mathfrak{a}} \left(ch L^{(0,1,0,2)}_{B_4}\right) = 6 \; ch L^{(0,0)}_{B_2}+ 60
  \; ch L_{B_2}^{(0,2)}+ 30 \; ch L_{B_2}^{(1,0)}+ 19 \; ch L_{B_2}^{(2,0)}+
  40 \; ch L_{B_2}^{(1,2)}+ 10 \; ch L_{B_2}^{(2,2)}.
\end{equation}

@@

Consider the affine extension of the example \ref{sec:regul-embedd-a_1}.
Since this embedding is regular, the level of the  subalgebra modules is equal to that of the initial module.

@@

Using the definition (\ref{fan-defined}) we get the fan $\Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$ with the corresponding values $s(\gamma+\gamma_0)$(see the Figure \ref{fig:AffineB2A1Fan}).
Here we restricted the computation to the twelfth grade.
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=130mm]{AffineB2_A1_fan.pdf}
  \caption{The fan for $\hat{A_1}\subset \hat{B_2}$}
  \label{fig:AffineB2A1Fan}
\end{figure}

@@

\begin{figure}[h!tb]
  \includegraphics[width=160mm]{AffineB2_A1_Anom.pdf}
  \caption{The anomalous weights of the $(1,0;1;0)$ representation of the algebra $\hat{B_2}$}
  \label{fig:affine_B2_anom_point}
\end{figure}

Performing the next step of the algorithm \ref{sec:algorithm} we project the anomalous weights to the weight space of the subalgebra $\hat{A_1}$ and find the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
The result of this computation up to the twelfth grade is presented in the Figure
\ref{fig:AffineB2_A1_anom_proj}.
\begin{figure}[p]
  \centering
  \includegraphics[width=120mm]{AffineB2_A1_proj_anom.pdf}
  \caption{The projected anomalous weights and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:AffineB2_A1_anom_proj}
\end{figure}

@@

There exist three level one dominant weights in the weight space of $\hat{A}_2$.
It is easy to see that the set $\Delta_{\bot}$ is empty and the subalgebra $\mathfrak{a}_{\bot}=0$.

@@

\begin{figure}[h!tb]
  \centering
  \includegraphics[width=180mm]{AffineA2_A1_anom.pdf}
  \caption{The anomalous weights of the module $L^{(0,0;1;0)}_{\hat{A_2}}$}
  \label{fig:affine_A2_anom_point}
\end{figure}

@@

The next step is to project the anomalous weights to $P_{\hat A_1}$.
The result up to the twelfth grade is presented in the Figure \ref{fig:AffineA2_A1_anom_proj}
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=150mm]{AffineA2_A1_proj_anom.pdf}
  \caption{Projected anomalous weights and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:AffineA2_A1_anom_proj}
\end{figure}

Using the recurrent relation for the anomalous branching coefficients we get the result presented in Figure \ref{fig:AffineA2_A1_branching}. 
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=110mm]{AffineA2_A1_branching.pdf}
  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{A_2}$}
  \label{fig:AffineA2_A1_branching}
\end{figure}

@@

Consider the embedding $\mathfrak{a}\subset \mathfrak{g}$ where $\mathfrak{a}=\widehat{su(2)}\oplus \widehat{su(2)}$ and $\mathfrak{g}= \widehat{su(4)}$, which is the affine extension of the special embedding $su(2)\oplus su(2)\subset su(4)$. Let's construct the special embedding $su(2)\oplus su(2)\subset su(4)$ using the method of \cite{vasilevich1986method}. We start with 4-dimensional representation of $su(2)\oplus su(2)$ with the highest weight $(1,1)$. The weights of this representation are numbered as depicted at the Figure \ref{fig:A_1+A_1_to_A3} and have the following coordinates in the fundamental weights basis: $\nu_1=(1,1),\; \nu_2=(-1,1),\; \nu_3=(1,-1),\; \nu_4=(-1,-1)$.

@@

We are interested in the reduction of the fundamental representations of $\widehat{su(4)}$.
Four dominant weights of level one have the following coordinates in the orthogonal basis: 
\begin{equation}
  \begin{array}{lll}
     \omega_0 & = & (0,0,0,0;1;0)\\
     \omega_1 & = & (\frac{3}{4},-\frac{1}{4},-\frac{1}{4},-\frac{1}{4}; 1; 0)\\
     \omega_2 & = & (\frac{1}{2},\frac{1}{2},-\frac{1}{2},-\frac{1}{2}; 1; 0)\\
     \omega_3 & = & (\frac{1}{4},\frac{1}{4},\frac{1}{4},-\frac{3}{4}; 1; 0) \\
  \end{array}
\end{equation}

These representation could be easily reduced by the method described in \cite{walton1989conformal}, which is based upon the properties of $A_n$-series of Lie algebras, but we use our general method and discuss its features.

@@

The set $\Delta^{+}_{\bot}$ is empty. 
The fan $\Gamma _{\frak{a}\subset \frak{g}}$ is shown at the Figure \ref{fig:A1+A1-A3_fan}. Coordinates of fan element's finite part are given in the basis of fundamental weights of $su(2)\oplus su(2)$. Element $\gamma$ is shown by cross if  $s(\gamma)=1$ and by diamond if $s(\gamma)=-1$.
\begin{figure}[h!tb]
  \includegraphics[width=150mm]{A1+A1-A3_fan.pdf}
  \caption{Fan for the special embedding $\widehat{su(2)}\oplus\widehat{su(2)}\subset \widehat{su(4)}$}
  \label{fig:A1+A1-A3_fan}
\end{figure}

We limit our computation by the fifth grade.
\begin{figure}[h!tb]
  \includegraphics[width=170mm]{A1+A1-A3_anom.pdf}
  \caption{Projected anomalous weights for $L^{\omega_1}_{A_3}$}
  \label{fig:A1+A1-A3_anom}
\end{figure}

The set  $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of the representation of the algebra $\hat{A}_3$ consists of 192 elements and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for $\mu=\omega_2=(0,0,1;1;0)$ is shown at the Figure \ref{fig:A1+A1-A3_anom}. Coordinates of anomalous weight's finite part are given in the basis of fundamental weights of $su(2)\oplus su(2)$. Weight $g$ are shown by cross if the corresponding value $\epsilon(\omega)=1$ and by diamond otherwise.

@@

The anomalous branching coefficients for the module $L^{(\omega_1)}$ are shown at the Figure  \ref{fig:A1+A1-A3_branching}.
\begin{figure}[h!tb]
  \includegraphics[width=180mm]{A1+A1-A3_branching.pdf}
  \caption{Anomalous branching coefficients for $L^{(0,0,1;1;0)}_{A_3}$}
  \label{fig:A1+A1-A3_branching}
\end{figure}

>>>>

All the cases are listed in the table \ref{tab:diagrams}.
\begin{table}[ph]
\label{tab:diagrams}
\noindent  \centering{
\begin{tabular}{|l|l|l|l|}
  \hline
  $\mathfrak{g}$ & Extended diagram of $\mathfrak{g}$ & Diagrams of the subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ \\
  \hline
  $A_n$ & \includegraphics{A_series_ext_diag.pdf} & \includegraphics{A_series_ext_split.pdf} \\
  \hline
  $B_n$ & \includegraphics{B_series_ext_diag.pdf} & \includegraphics{B_series_ext_split.pdf} \\
  \hline
  $C_n$ & \includegraphics{C_series_ext_diag.pdf} & \includegraphics{C_series_ext_split.pdf} \\
  \hline
  $D_n$ & \includegraphics{D_series_ext_diag.pdf} & \includegraphics{D_series_ext_split.pdf} \\
  \hline
\end{tabular}
\caption{Subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ for the classical series}}
\end{table}

@@

For the coefficient function $s\left( \gamma \right) $ define the carrier $\Phi _{\frak{a%
}\subset \frak{g}}\subset P_{\frak{a}}$:
\begin{equation}
\Phi _{\frak{a}\subset \frak{g}}=\left\{ \gamma \in P_{\frak{a}}\mid s\left(
\gamma \right) \neq 0\right\} .  \label{phi-d}
\end{equation}
From the obtained equation for the formal elements,
\begin{multline}
  \label{eq:16}
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}=\\
  = -\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s\left( \gamma \right) e^{-\gamma }\sum_{\lambda \in P_{\frak{a}}}
  k_{\lambda }^{\left( \mu \right) }e^{\lambda } \\
  =-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}}\sum_{\lambda \in P_{\frak{a}}}s\left( \gamma \right) k_{\lambda }^{\left( \mu \right)}e^{\lambda -\gamma }
\end{multline}
we can deduce the following property of the anomalous branching coefficients,
\begin{multline}
  \label{eq:17}
   \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
   \sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}} s(\gamma)\; k^{(\mu)}_{\xi+\gamma}=0;\\ \xi\in P_{\mathfrak{a}}.
\end{multline}

@@

\subsubsection{Embedding of $B_2$ into $B_4$}
\label{sec:someth-high-dimens}
Consider the regular embedding $B_2 \longrightarrow B_4$.
We calculate the branching coefficients for the fundamental vector representation of $B_4$.
The corresponding Dynkin diagrams are in the Figure \ref{fig:dynkin}.
\begin{figure}[ph]
  \centering
  \includegraphics[width=60mm]{B4_B2_2A1.pdf}
  \caption{Dynkin diagrams for the regular embedding $B_2\subset B_4$. Note the dropped node and the roots of $\mathfrak{a}_{\bot}$. }
  \label{fig:dynkin}
\end{figure}

@@

The result of this procedure is shown in the Figure \ref{fig:B4B2anom}.
\begin{figure}[h!tb]
  \centering
    \includegraphics[width=100mm]{B4_B2_anom_points.pdf}
  \caption{Projected weights of $\pi_{B_2}\left(\Psi^{(0,1,0,2)}_{B_4}\right)$ with the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:B4B2anom}
\end{figure}

\begin{figure}[h!tb]
  \centering
  \includegraphics[width=80mm]{B4_B2_fan.pdf}
  \caption{The fan for $B_2\subset B_4$}
  \label{fig:B4B2Fan}
\end{figure}
Applying the recurrent relation (\ref{recurrent-relation}) we obtain the
following branching coefficients:
\begin{multline}
  \label{eq:24}
  \pi_{\mathfrak{a}} \left(ch L^{(0,1,0,2)}_{B_4}\right) = 6 \; ch L^{(0,0)}_{B_2}+ 60
  \; ch L_{B_2}^{(0,2)}+ 30 \; ch L_{B_2}^{(1,0)}+ 19 \; ch L_{B_2}^{(2,0)}+\\
  40 \; ch L_{B_2}^{(1,2)}+ 10 \; ch L_{B_2}^{(2,2)}.
\end{multline}

@@

Consider the affine extension of the example \ref{sec:regul-embedd-a_1}.
Since this embedding is regular and $x_e=1$, the level of the  subalgebra modules is equal to that of the initial module.

@@

Using the definition (\ref{fan-defined}) we get the fan $\Gamma_{\hat{A_1} \longrightarrow  \hat{B_2} }$ with the corresponding values $s(\gamma+\gamma_0)$(see the Figure \ref{fig:AffineB2A1Fan}).
Here we restricted the computation to the twelfth grade.
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=135mm]{AffineB2_A1_fan.pdf}
  \caption{The fan for $\hat{A_1}\subset \hat{B_2}$}
  \label{fig:AffineB2A1Fan}
\end{figure}

@@

\begin{figure}[h!tb]
  \hspace*{-2cm}
  \includegraphics[width=200mm]{AffineB2_A1_Anom.pdf}
  \caption{The anomalous weights of the $(1,0;1;0)$ representation of the algebra $\hat{B_2}$}
  \label{fig:affine_B2_anom_point}
\end{figure}

Performing the next step of the algorithm \ref{sec:algorithm} we project the anomalous weights to the weight space of the subalgebra $\hat{A_1}$ and find the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
The result of this computation up to the twelfth grade is presented in the Figure
\ref{fig:AffineB2_A1_anom_proj}.
\begin{figure}[p]
  \centering
  \includegraphics[width=120mm]{AffineB2_A1_proj_anom.pdf}
  \caption{The projected anomalous weights $\pi_{\hat A_1}\left(\Psi^{(1,0;1;0)}_{\hat B_2}\right)$ and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:AffineB2_A1_anom_proj}
\end{figure}

@@

There exist three level one fundamental weights in the weight space of $\hat{A}_2$.
It is easy to see that the set $\Delta_{\bot}$ is empty and the subalgebra $\mathfrak{a}_{\bot}=0$.

@@

\begin{figure}[h!tb]
%  \hspace*{-2cm}
  \includegraphics[width=140mm]{AffineA2_A1_anom.pdf}
  \caption{The anomalous weights of the module $L^{(0,0;1;0)}_{\hat{A_2}}$}
  \label{fig:affine_A2_anom_point}
\end{figure}

@@

The next step is to project the anomalous weights to $P_{\hat A_1}$.
The result up to the twelfth grade is presented in the Figure \ref{fig:AffineA2_A1_anom_proj}
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=130mm]{AffineA2_A1_proj_anom.pdf}
  \caption{Projected anomalous weights of $L^{(0,0;1;0)}_{\hat{A_2}}$.}
  \label{fig:AffineA2_A1_anom_proj}
\end{figure}

Using the recurrent relation for the anomalous branching coefficients we get the result presented in Figure \ref{fig:AffineA2_A1_branching}. 
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=130mm]{AffineA2_A1_branching.pdf}
  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{A_2}$}
  \label{fig:AffineA2_A1_branching}
\end{figure}

@@

Consider the embedding $\mathfrak{a}\subset \mathfrak{g}$ where $\mathfrak{a}=\hat A_1\oplus \hat A_1$ and $\mathfrak{g}= \hat A_3$, which is the affine extension of the special embedding $su(2)\oplus su(2)\subset su(4)$. Let's construct the special embedding $su(2)\oplus su(2)\subset su(4)$ using the method of \cite{vasilevich1986method}. We start with 4-dimensional representation of $su(2)\oplus su(2)$ with the highest weight $(1,1)$. The weights of this representation are numbered as depicted at the Figure \ref{fig:A_1+A_1_to_A3} and have the following coordinates in the fundamental weights basis: $\nu_1=(1,1),\; \nu_2=(-1,1),\; \nu_3=(1,-1),\; \nu_4=(-1,-1)$.

@@

We are interested in the reduction of the fundamental modules of $\widehat{su(4)}$.
Four fundamental weights of level one have the following coordinates in the orthogonal basis: 
\begin{equation}
  \begin{array}{lll}
     \omega_0 & = & (0,0,0,0;1;0)\\
     \omega_1 & = & (\frac{3}{4},-\frac{1}{4},-\frac{1}{4},-\frac{1}{4}; 1; 0)\\
     \omega_2 & = & (\frac{1}{2},\frac{1}{2},-\frac{1}{2},-\frac{1}{2}; 1; 0)\\
     \omega_3 & = & (\frac{1}{4},\frac{1}{4},\frac{1}{4},-\frac{3}{4}; 1; 0) \\
  \end{array}
\end{equation}

These modules could be easily reduced by the method described in \cite{walton1989conformal}, which is based upon the properties of $A_n$-series of Lie algebras, but we use our general method and discuss its features.

@@

The set $\Delta^{+}_{\bot}$ is empty. 
The fan $\Gamma _{\frak{a}\subset \frak{g}}$ is shown at the Figure \ref{fig:A1+A1-A3_fan}. Coordinates of fan element's finite part are given in the basis of fundamental weights of $su(2)\oplus su(2)$. Element $\gamma$ is shown by cross if  $s(\gamma)=1$ and by diamond if $s(\gamma)=-1$.
\begin{figure}[h!tb]
  \includegraphics[width=135mm]{A1+A1-A3_fan.pdf}
  \caption{Fan for the special embedding $\hat A_1\oplus\hat A_1\subset\hat A_3$}
  \label{fig:A1+A1-A3_fan}
\end{figure}

We limit our computation by the fifth grade.
\begin{figure}[h!tb]
  \hspace*{-1cm}
  \includegraphics[width=170mm]{A1+A1-A3_anom.pdf}
  \caption{Projected anomalous weights for $L^{\omega_1}_{\hat A_3}$}
  \label{fig:A1+A1-A3_anom}
\end{figure}

The set  $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of the module of the algebra $\hat{A}_3$ consists of 192 elements and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for $\mu=\omega_2=(0,0,1;1;0)$ is shown at the Figure \ref{fig:A1+A1-A3_anom}. Coordinates of anomalous weight's finite part are given in the basis of fundamental weights of $su(2)\oplus su(2)$. Weight $g$ are shown by cross if the corresponding value $\epsilon(\omega)=1$ and by diamond otherwise.

@@

The anomalous branching coefficients for the module $L^{(\omega_1)}$ are shown at the Figure  \ref{fig:A1+A1-A3_branching}.
\begin{figure}[h!tb]
%  \hspace*{-1cm}
  \includegraphics[width=135mm]{A1+A1-A3_branching.pdf}
  \caption{Anomalous branching coefficients for $L^{(0,0,1;1;0)}_{\hat A_3}$}
  \label{fig:A1+A1-A3_branching}
\end{figure}
